\documentclass[10pt]{article}

\usepackage[top=0.32in,bottom=0.32in,left=0.5in,right=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage{microtype}

\setmainfont{TeX Gyre Termes}

\definecolor{accent}{HTML}{1F3A5F}
\definecolor{muted}{HTML}{555555}

\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\linespread{0.95}

% Section headings
\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\vspace{1pt}\color{accent}\titlerule\vspace{1pt}]
\titlespacing*{\section}{0pt}{2pt}{2pt}

% Entry: bold title on left, date on right
\newcommand{\entry}[2]{\textbf{#1}\hfill{\color{muted}#2}\par}
\newcommand{\subentry}[1]{{\itshape #1}\par}

\setlist[itemize]{leftmargin=1.3em, topsep=0pt, itemsep=0.5pt, parsep=0pt, label=\textbullet}

\begin{document}

%==================== HEADER ====================
\begin{center}
    {\Huge\bfseries\color{accent} YASHU SHUKLA}\\[2pt]
    {\normalsize Data Scientist \ $\cdot$\ ML Engineer \ $\cdot$\ Hanyang University}\\[2pt]
    {\small
    \href{mailto:yashushukla2014@gmail.com}{yashushukla2014@gmail.com} \ $\vert$\ \ +82-2177-8965 \ $\vert$\ \ Seoul, South Korea \ $\vert$\ \ \href{https://github.com/ys2064}{github.com/ys2064}}
\end{center}

\vspace{-4pt}

%==================== EDUCATION ====================
\section{Education}
\entry{B.E. in Data Science \ $\vert$\ Hanyang University, South Korea}{2022 -- 2026}
Major: Data Science Engineering \& Physiological Brain Science \quad$\vert$\quad GPA: 4.0 / 4.5\par
\vspace{1pt}
\entry{High School \ $\vert$\ Vibgyor High School, India (Science)}{2015 -- 2022}
Top 5 in Grade 12 (92.6\%) \quad$\vert$\quad Top 10 in Grade 10 (93.5\%)\par
\vspace{1pt}
\entry{Primary School \ $\vert$\ International School of Koje, South Korea}{2008 -- 2015}

%==================== TECHNICAL SKILLS ====================
\section{Technical Skills}
\textbf{Languages:} Python, C, C++, R, JavaScript, TypeScript\par
\textbf{Frameworks / Tools:} PyTorch, TensorFlow, scikit-learn, Keras, NumPy, pandas, Matplotlib, Seaborn, Django, ROS, ELK Stack, Angular 10\par
\textbf{Robotics / Cloud / DB:} Isaac Sim/Lab, Robot Manipulation, 3D Object Scanning, AWS, GCP, SQL, PostgreSQL\par

%==================== EXPERIENCE ====================
\section{Experience}
\entry{AI Research Engineer Intern \ $\vert$\ RLWRLD, Seoul}{Dec 2025 -- Present}
\begin{itemize}
    \item Built and curated robotic interaction datasets in Isaac Sim, including 3D object scanning, simulation environments, and data preparation.
    \item Trained and evaluated VLA models (GR00T, Pi) for robotic manipulation tasks.
    \item Optimized dataset composition and distribution for Robot Foundation Model (RFM) training; contributing to a dexterous-first RFM for humanoid robotics.
\end{itemize}
\vspace{1pt}
\entry{Data Science Intern \ $\vert$\ w3company, Seoul}{Mar 2025 -- Dec 2025}
\begin{itemize}
    \item Built an ML-driven multi-module fake-account \& anomaly detection system (patent filed); trained ResNet classifiers to detect AI-generated profile photos and fraudulent identities.
    \item Developed and evaluated BERT-based NLP models for sentiment analysis and text classification for a social networking app (Moji), extracting user-engagement insights from large datasets.
\end{itemize}
\vspace{1pt}
\entry{Teaching Assistant \ $\vert$\ Hanyang University, Seoul}{Sep -- Dec 2024}
\begin{itemize}
    \item Managed a class of 30+ students for ``Understanding Business Environment''; facilitated group discussions and class activities.
\end{itemize}
\vspace{1pt}
\entry{Software Engineer Intern \ $\vert$\ Bespoke System Pvt. Ltd., India}{Jul -- Aug 2024}
\begin{itemize}
    \item Full-stack web development with ASP.NET, MS SQL, Angular 10, and Web API; focused on API integration and database management.
\end{itemize}

%==================== PUBLICATIONS ====================
\section{Publications \& Conferences}
\begin{itemize}
    \item \textbf{Research Contributor} --- ``RLDX-1 Technical Report'' (arXiv), May 2026. VLA systems \& Robot Foundation Models for dexterous humanoid manipulation; end-to-end automated training and inference pipeline.
    \item \textbf{Poster Presenter} --- ``Cerebellum Activation in Depression,'' Korean Society for Brain and Neural Sciences (KSBNS), Aug 2025.
    \item \textbf{Research Attendee} --- 12th Swiss-Korean Life Science Symposium, Seoul, May 2025.
\end{itemize}

%==================== PROJECTS ====================
\section{Projects}
\entry{Stress Detection via mmWave Radar}{Mar -- Dec 2025}
Contactless health vitals monitoring using mmWave radar; denoised vital-sign data for feature extraction.\par
\vspace{1pt}
\entry{StressMate --- Mental Wellness App}{May -- Jun 2025}
Django + LLMs (Perplexity, Gemini) with RAG, deployed on AWS EC2/S3.\par
\vspace{1pt}
\entry{Cerebellar fMRI Analysis in MDD}{May -- Jun 2025}
fMRI analysis revealing significantly reduced cerebellar response to positive stimuli in MDD patients vs.\ controls.\par
\vspace{1pt}
\entry{PlateCheck}{Oct -- Dec 2024}
LLM-based Korean food ingredient recognition using fine-tuned ResNet + GPT-4o Mini; HCI user study evaluation.\par
\vspace{1pt}
\entry{Food Demand Forecasting}{Oct -- Dec 2024}
Time-series model using Temporal Convolutional Network (TCN) on historical sales data.\par
\vspace{1pt}
\entry{News Audio Summarizer}{Sep -- Dec 2024}
NLP pipeline converting audio news to text with fine-tuned BART summarization.\par

%==================== SCHOLARSHIPS ====================
\section{Scholarships \& Achievements}
\entry{Hanyang Brain (Academic Excellence) Scholarship \ $\vert$\ Awarded 3 consecutive semesters}{2025 -- 2026}
\vspace{1pt}
\entry{Daewoong Foundation Global Scholarship}{Nov 2025 -- Mar 2026}
\vspace{1pt}
\entry{Special Scholarship for Academic Encouragement -- Foreigner, Hanyang University}{Sep -- Dec 2024}

%==================== LANGUAGES ====================
\section{Languages \& Extracurricular}
\textbf{Languages:} English \& Hindi (Native) \ $\vert$\ Gujarati (Intermediate) \ $\vert$\ Korean (Beginner)\par
\textbf{Activities:} Basketball \& Badminton \ $\vert$\ Dance: Kathak Senior Diploma (5 yrs) \ $\vert$\ Indian Embassy Performer, Seoul\par

\end{document}
